R tools for accessing research literature for text mining

### 2019-05-06 manuscript.Rmd
Typo

---
layout: review, 11pt
linenumbers: true
title: "R tools for accessing research literature for text mining"
author:
  - name: Scott Chamberlain
    affiliation: cstar
    email: myrmecocystus(at)gmail.com
    footnote: Corresponding author
address:
  - code: cstar
    address: |
      rOpenSci, Museum of Paleontology, University of California, Berkeley, CA, USA
abstract: |
  Text-mining is a powerful method for answering research questions. However,
  getting texts to extract information can be a daunting and complicated task.
  The primary reason for this is publishers. There are thousands of different
  publishers, each with their own licenses, URL patterns, access options, and
  more. Layered on top of that is the varied access each user has based on
  their institutional affiliation. Here, I introduce a suite of software packages
  in the R programming language for fetching texts. The tapestry of different
  publishers, access levels, and other factors requires a patchwork of approaches
  for getting texts to users. The flagship R package called fulltext attempts
  to simplify search and retrieval of texts for text-mining. The fulltext package,
  along with many others, make acquiring texts easier than ever, facilitating
  answering research questions with text-mining.
bibliography: components/references.bib
csl: components/peerj.csl
documentclass: components/elsarticle
output:
  pdf_document:
    template: components/elsarticle.latex
    keep_tex: true
    fig_caption: true
---

@@

There's more than 100 million research articles published
(Crossref API: <https://github.com/CrossRef/rest-api-doc>), representing
an enormous amount of knowledge. In addition to simply reading these
articles, the articles contain a vast trove of information of interest to
researchers for machine aided questions [@Kong2018; @Usai2018]. For example,
many researchers are interested in statistical outcomes of articles that 
can be extracted from numeric results: P-values, effect sizes, means, and
more. In addition, researchers are often interested in words in articles,
their use through time, and the contexts they are found in.

Text-mining is the broad term associated with pulling information
out of articles. Given the importance of text-mining, good
text-mining tools are needed to make it easier for researchers to do.
Graphical user interface (GUI) based text mining tools are available
[e.g., @ba2016interoperability; @Munoz2019; @Canada2017] and some research papers
have used them [@Chaix2019], but given the urgent recent call to action for
more reproducible research [@OSC2015; @Camerer2016; @Camerer2018],
we must move away from GUI based tools as fast as possible. A number of examples
of programmatic tools can be found in the literature. For example, @Sinclair2016
present a tool in Python called seqenv for the domain specific task of
linking sequences to environments through text mining.

Most recent text-mining papers do not use programmatic approaches, highlighting
the need for more programmatic text-mining tools, and increased
discussion of those tools to increase awareness. For example, many papers 
search Web of Science using their web interface, and downloading papers manually 
[@Ding2018; @McCallen2019]. Many of these papers doing GUI based searching and 
paper downloads are using R or Python downstream for analysis; replacing 
GUI based data acquisition with programmatic approaches will improve 
research.

The R programming language is used widely throughout many academic fields;
tools in R for text mining are of particular importance because they
can be adopted by academics rapidly.

Here, I present an overview of text-mining tools in the R programming
language, not for text-mining analysis, but rather those
tools for searching for, acquiring, and extracting parts of texts
(e.g., title, abstract, authors). Most of the packages presented here are
part of the rOpenSci suite (https://ropensci.org/).

@@

Of the non-machine readable types, the most noteable is the Portable
Document Format (PDF)[^pdf]. These can be broken out into two groups: text based
PDFs and scanned PDFs. The former are converted from digital versions of
various kinds (MS Word, OpenOffice, LaTeX, markdown, etc.), while the
latter are created by scanning print articles to a PDF format. Text-based
PDFs are much better for text-mining purposes as plain text can be extracted
easily in R with [pdftools][], a binding to [libpoppler][]. However, with
scanned PDFs, text must be extracted using Optimal Character Recognition
(OCR; see R package [tesseract][]), which isn't always a clean solution,
especially compared to true text based PDFs.

The reality in scholarly publishing is all publishers, if they provide
any access to their articles, only provide PDF format. Very few publishers,
with some quite large (Elsevier, Pensoft, PLOS), provide XML format. Although
most publishers most likely have the XML behind each of their articles,
they for some indefensible reason do not share it - making text-mining more
difficult. Some provide plain text (Elsevier). I only know of one publisher
that provides full text as JSON (PLOS). Thus, text-mining, in most cases,
will require extracting text from PDFs.

@@

Acces to full-text is the holy grail in text-mining. Some use cases can
get by with article metadata (authors, title, etc.), some with abstracts,
but many use cases require full-text.

@@

Some may not realize access to articles varies with IP address so that
access from campus vs. from home (if not on a VPN) will drastically differ.
Sometimes a VPN is required, and this can provide a significant technical
hurdle to users attempting to do text-mining work.

One final hurdle in text-mining comes unsurprisingly from Elsevier. They
use so-called "fences" for programmatic access. That is, even if a person
trying to get an article programmatically their institution has access to
and they have access to, and they are on the correct IP address, they may
still not get access to an Elsevier article. Elsevier puts in place these
fences and only if you contact their technical team directly can you
get these fences removed, and only then on a per institution basis.

@@

A text-mining project starts with a question. From that question, researchers
then attempt to acquire scholarly articles for text-mining. Finding appropriate
articles is not altogether straight-forward.

@@

On top of the vast array of different data sources is the varied ways that 
search is implemented in each source. Most sources are probably using Solr
or Elasticsearch under the hood, though we can't know this for sure as most 
do not make their software infrastructure public knowledge. Nonetheless, data
sources differ in how search works from the user perspective. For example, some 
provide wild card search and some do not. Some sources are searching full text
of articles, while others only search metadata (i.e., title, authors, abstract).
In addition, each source has a different set of metadata/full text available.
In brief, the same search against different sources produces different results.
Some text-mining research articles perform the same search against many
different sources (refs), while others choose just one source.

@@

There is increasing open access scientific literature content available
online. However, only a small proportion of scientific journals provide
access to their full content; whereas, most publishers provide open
access to their metadata only (most often through Crossref; Table 1).
The following is a synopsis of the major data sources and associated R
tools.

@@

Data Provider                      | Content Type            | rOpenSci Package         | Documentation
---------------------------------- | ---------------------   | ------------------------ | -------------
Crossref                           | Metadata                | rcrossref/crminer        | [^1]
DataCite                           | Metadata                | rdatacite                | [^2]
Biodiversity Heritage Library      | Full content/Metadata   | rbhl                     | [^3]
Public Library of Science (PLoS)   | Full content/altmetrics | rplos                    | [^4]
Scopus (Elsevier)                  | Full content/Metadata   | fulltext                 | [^5]
arXiv                              | Full content/Metadata   | aRxiv                    | [^6]
Biomed Central (via Springer)      | Full content/Metadata   | fulltext                 | [^7]
bioRxiv                            | Full content/Metadata   | fulltext                 | [^8]
PMC/Pubmed (via Entrez)            | Full content/Metadata   | rentrez                  | [^9]
Europe PMC                         | Full content/Metadata   | europepmc                | [^10]
Microsoft Academic Search          | Metadata                | microdemic               | [^11]
Directory of Open Access Journals  | Metadata                | jaod                     | [^12]
JSTOR Data for Research            | Full content            | jstor                    | [^13]
ORCID                              | Metadata                | rorcid                   | [^14]
Wikimedia's Citoid                 | Citations               | rcitoid                  | [^15]
Open Citation Corpus               | Citations               | citecorp                 | [^16]
Fatcat                             | Metadata                | none                     | [^17]
SHERPA/RoMEO                       | Journal Level Metadata  | rromeo                   | [^18]
CORE                               | Full content/Metadata   | rcoreoa                  | [^19]
Dissemin                           | Metadata                | dissemr                  | [^20]

@@

## Crossref/Datacite

@@

One can search by DOI or search citation data to get citations. In addition, Crossref has a
text-mining opt-in program for publishers. The result of this is that some
publishers provide URLs for full text content of their articles. The majority of these links
are pay-walled, while some are open access. Using any of the various tools for working with
Crossref data, you can filter your search to get only articles with full text links, and further
to get only articles with full text links that are open access.

The main interfaces for Crossref in R are [rcrossref][] and [crminer][]. Similar interfaces
are available in Ruby ([serrano][]) and Python ([habanero][]).

@@

Elsevier is one of the largest publishers. Most of their articles are not open access. However,
they have a numbrer of advantages if you have access to their articles: they are one of the few
publishers to provide machine readable XML (many publishers do have XML versions of articles,
but do not provide it); they are one of the few (two) publishers part of Crossref's text
and data mining program. The packages [fulltext][] and [crminer][] can be used to access
Elsevier articles through Crossref's TDM program. There's an interface to Scopus article
search within [fulltext][].

@@

arXiv and bioRxiv are preprint publishers, the former in existence for many years, and the
latter new on the scene. You can access articles from these publishers through [fulltext][].
arXiv does provide a web API that we hook into; bioRxiv does not, but we can get you
articles nonetheless.

@@

Fatcat is a project from Ben Newbold of the Internet Archive Labs. It is a 
"versioned, publicly-editable catalog of research publications:  journal articles,
conference proceedings, pre-prints, blog posts". Fatcat is currently does not have an
R client, but is used inside of the [fulltext][] package.

@@

@@

[fulltext][] is a general purpose R package for the data part of text-mining:
search for articles, get links to articles, get article abstracts, and fetch
full text of articles. The `fulltext` package is always adding additional
data sources as time allows (See Table 1). Starting from searching for
articles, the outputs of search can be fed into a function to get links
to those articles, or to get abstracts for those articles, or to fetch
their full text. The following is a breakdown of the major distinct
parts of `fulltext`.

@@

Since users can go through a lot of article requests, we cache successfully
downloaded articles, and keep that knowledge consistent across R sessions; all
subsequent requests for the same article just use the cached version. Additionally,
all errors in `ft_get()` are collected in a tidy data.frame in the output of the
function to help the user quickly determine what went wrong.

# How to text mine from R: Three case studies

## Case study 1: Citation mining

@@

## Case study 2: Abstract mining

@@

## Case study 3: Full text mining

@@

Text-mining will always be a complex task given all the layers involved:
often temporal time-span of research questions; varied permissions among 
researchers and their articles they're trying to access; varied approaches
to getting full text (xml vs pdf vs plain text); and more.

Programmatic text-mining is a first step towards making text-mining easier.
The R ecosystem is an especially good place to do text-mining because 
there are many packages for text-mining analysis, and endless packages for
any required statistical analyses. In addition, rOpenSci and others are 
building up a set of packages in R for searching for and acquiring full
text programatically to help make the research workflow as reproducible
as possible.

@@

With respect to what publishers can do to make text-mining easier, publishers
should:

@@

xxxx

@@

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier (DOI). This DOI
corresponds to a snapshot of the GitHub repository at
<https://github.com/ropensci/textmine>. Software can be found at
<https://github.com/ropensci/xxx>, xxxx, all under MIT licenses.

@@

[rcrossref]: https://github.com/ropensci/rcrossref
[rorcid]: https://github.com/ropensci/rorcid
[fulltext]: https://github.com/ropensci/fulltext
[microdemic]: https://github.com/ropensci/microdemic
[arXiv]: https://github.com/ropensci/arXiv
[rdatacite]: https://github.com/ropensci/rdatacite
[rbhl]: https://github.com/ropensci/rbhl
[rentrez]: https://github.com/ropensci/rentrez
[rplos]: https://github.com/ropensci/rplos
[crminer]: https://github.com/ropensci/crminer
[europepmc]: https://github.com/ropensci/europepmc
[jaod]: https://github.com/ropensci/jaod
[jstor]: https://github.com/ropensci/jstor
[rcitoid]: https://github.com/ropenscilabs/rcitoid
[citecorp]: https://github.com/ropenscilabs/citecorp
[serrano]: https://github.com/sckott/serrano
[habanero]: https://github.com/sckott/habanero
[quanteda]: https://quanteda.io/
[pubchunks]: https://github.com/ropensci/pubchunks
[pdftools]: https://github.com/ropensci/pdftools
[libpoppler]: https://poppler.freedesktop.org/
[tesseract]: https://github.com/ropensci/tesseract
[rcoreoa]: https://github.com/ropensci/rcoreoa

>>>>

---
layout: review, 11pt
linenumbers: true
title: "R tools for accessing research literature for text mining"
author:
  - name: Scott Chamberlain
    affiliation: cstar
    email: myrmecocystus(at)gmail.com
    footnote: Corresponding author
address:
  - code: cstar
    address: |
      rOpenSci, Museum of Paleontology, University of California, Berkeley, CA, USA
abstract: |
  Text mining is a powerful method for answering research questions. However,
  getting texts to extract information can be a daunting and complicated task.
  The primary reason for this is the diversity of publisher technologies.
  There are thousands of different publishers, each with their own licenses,
  URL patterns, access options, and more. Layered on top of that is the varied
  access each user has based on their institutional affiliation. Here, I
  introduce a suite of software packages in the R programming language for
  fetching texts. The tapestry of different publishers, access levels, and
  other factors requires a patchwork of approaches for getting texts to users.
  The flagship R package called fulltext attempts to simplify search and
  retrieval of texts for text mining by serving as an interface to the varied
  and complex publishers. The fulltext package, along with many others, make
  acquiring texts easier than ever, facilitating answering research questions
  with text mining.
bibliography: components/references.bib
csl: components/peerj.csl
documentclass: components/elsarticle
output:
  pdf_document:
    template: components/elsarticle.latex
    keep_tex: true
    fig_caption: true
---

@@

There are more than 100 million research articles published
(Crossref API: <https://github.com/CrossRef/rest-api-doc>), representing
an enormous amount of knowledge. In addition to simply reading these
articles, the articles contain a vast trove of information of interest to
researchers for machine aided questions [@Kong2018; @Usai2018]. For example,
many researchers are interested in statistical outcomes of articles that
can be extracted from numeric results: P-values, effect sizes, means, and
more. In addition, researchers are often interested in words in articles,
their use through time, and the contexts they are found in.

Text mining is the broad term associated with pulling information
out of articles. Given the importance of text mining, good
text mining tools are needed to make it easier for researchers to do.
Graphical user interface (GUI) based text mining tools are available
[e.g., @ba2016interoperability; @Munoz2019; @Canada2017] and some research papers
have used them [@Chaix2019], but given the urgent recent call to action for
more reproducible research [@OSC2015; @Camerer2016; @Camerer2018],
we must move away from GUI based tools as fast as possible. A number of examples
of programmatic tools can be found in the literature. For example, @Sinclair2016
present a tool in Python called seqenv for the domain specific task of
linking sequences to environments through text mining.

Using programmatic tools for text mining is important for a variety of reasons.
First, using programmatic tools makes it easier for yourself. You can re-run code
to get updated results as data changes, and results can always be re-created.
Second, code can be shared whereas GUI driving workflows can not; colleagues,
reviewers and other researchers can reproduce and check your work. (FIXME: 
re-work this; citations)

Most recent text mining papers do not use programmatic approaches, highlighting
the need for more programmatic text mining tools, and increased
discussion of those tools to increase awareness. For example, many papers
search Web of Science using their web interface, and downloading papers manually
[@Ding2018; @McCallen2019]. Many of these papers doing GUI based searching and
paper downloads are using R or Python downstream for analysis; replacing
GUI based data acquisition with programmatic approaches will improve
research.

The R programming language is free of cost, and is used widely throughout
many academic fields; tools in R for text mining are of particular
importance because they can be adopted by academics rapidly.

Here, I present an overview of text mining tools in the R programming
language, not for text mining analysis, but rather those
tools for searching for, acquiring, and extracting parts of texts
(e.g., title, abstract, authors). Most of the packages presented here are
part of the rOpenSci suite (https://ropensci.org/).

@@

Of the non-machine readable types, the most noteable is the Portable
Document Format (PDF)[^pdf]. These can be broken out into two groups: text based
PDFs and scanned PDFs (images of text). The former are converted from digital
versions of various kinds (MS Word, OpenOffice, LaTeX, markdown, etc.), while the
latter are created by scanning print articles to a PDF format. Text-based
PDFs are much better for text mining purposes as plain text can be extracted
easily in R with [pdftools][], a binding to [libpoppler][]. However, with
scanned PDFs, text must be extracted using Optimal Character Recognition
(OCR; see R package [tesseract][]), which isn't always a clean solution,
especially compared to true text based PDFs.

The reality in scholarly publishing is all publishers, if they provide
any access to their articles, only provide PDF format. Very few publishers,
with some quite large (Elsevier, Pensoft, PLOS), provide XML format. Although
most publishers most likely have the XML behind each of their articles,
they for some indefensible reason do not share it - making text mining more
difficult. Some provide plain text (Elsevier). I only know of one publisher
that provides full text as JSON (PLOS). Thus, text mining, in most cases,
will require extracting text from PDFs.

@@

Acces to full-text is the holy grail in text mining. Some use cases can
get by with article metadata (authors, title, etc.), some with abstracts,
but many use cases require full-text.

@@

Some may not realize access to articles varies with IP address so that
access from campus vs. from home (if not on a VPN) will drastically differ.
Sometimes a VPN is required, and this can provide a significant technical
hurdle to users attempting to do text mining work.

One final hurdle in text mining comes unsurprisingly from Elsevier. They
use so-called "fences" for programmatic access. That is, even if a person
trying to get an article programmatically their institution has access to
and they have access to, and they are on the correct IP address, they may
still not get access to an Elsevier article. Elsevier puts in place these
fences and only if you contact their technical team directly can you
get these fences removed, and only then on a per institution basis.

@@

A text mining project starts with a question. From that question, researchers
then attempt to acquire scholarly articles for text mining. Finding appropriate
articles is not altogether straight-forward.

@@

On top of the vast array of different data sources is the varied ways that
search is implemented in each source. Most sources are probably using Solr
or Elasticsearch under the hood, though we can't know this for sure as most
do not make their software infrastructure public knowledge. Nonetheless, data
sources differ in how search works from the user perspective. For example, some
provide wild card/fuzzy search (i.e., 'appl\*' includes results for 'apple',
'application', etc.) and some do not. Some sources are searching full text
of articles, while others only search metadata (i.e., title, authors, abstract).
In addition, each source has a different set of metadata/full text available.
In brief, the same search against different sources produces different results.
Some text mining research articles perform the same search against many
different sources (refs), while others choose just one source.

@@

There is increasing open access scientific literature content available
online. However, only a small proportion of scientific journals provide
access to their full text; whereas, most publishers provide open
access to their metadata only (most often through Crossref; Table 1).
The following is a synopsis of the major data sources and associated R
tools.

@@

Data Provider                      | Content Type                 | rOpenSci Package   | Documentation
---------------------------------- | ---------------------------- | ------------------ | -------------
Crossref                           | Metadata                     | rcrossref/crminer  | [^1]
DataCite                           | Metadata                     | rdatacite          | [^2]
Biodiversity Heritage Library      | Full text/Metadata           | rbhl               | [^3]
Public Library of Science (PLoS)   | Full text (pdf/xml)/Metadata | rplos              | [^4]
Scopus (Elsevier)                  | Full text (pdf/xml)/Metadata | fulltext           | [^5]
arXiv                              | Full text (pdf)/Metadata     | aRxiv              | [^6]
Biomed Central (via Springer)      | Full text (pdf)/Metadata     | fulltext           | [^7]
bioRxiv                            | Full text (pdf)/Metadata     | fulltext           | [^8]
PMC/Pubmed (via Entrez)            | Full text (pdf/xml)/Metadata | rentrez            | [^9]
Europe PMC                         | Full text (pdf/xml)/Metadata | europepmc          | [^10]
Microsoft Academic Search          | Metadata                     | microdemic         | [^11]
Directory of Open Access Journals  | Metadata                     | jaod               | [^12]
JSTOR Data for Research            | Full text                    | jstor              | [^13]
ORCID                              | Metadata                     | rorcid             | [^14]
Wikimedia's Citoid                 | Citations                    | rcitoid            | [^15]
Open Citation Corpus               | Citations                    | citecorp           | [^16]
Fatcat                             | Metadata                     | none               | [^17]
SHERPA/RoMEO                       | Journal Level Metadata       | rromeo             | [^18]
CORE                               | Full text (pdf)/Metadata     | rcoreoa            | [^19]
Dissemin                           | Metadata                     | dissemr            | [^20]

@@

## Crossref and Datacite

@@

One can search by DOI or search citation data to get citations. In addition, Crossref has a
text mining opt-in program for publishers. The result of this is that some
publishers provide URLs for full text content of their articles. The majority of these links
are pay-walled, while some are open access. Using any of the various tools for working with
Crossref data, you can filter your search to get only articles with full text links, and further
to get only articles with full text links that are open access.

The main interfaces for Crossref in R are [rcrossref][] and [crminer][]. rcrossref is a
complete client for the public facing Crossref web services including metadata, whereas crminer
focuses only on retrieving full text of articles. Similar interfaces to rcrossref
are available in Ruby ([serrano][]) and Python ([habanero][]).

@@

Elsevier is one of the largest publishers. Scopus is one of their products, a searchable
database of articles. Most of their articles are not open access. However,
they have a number of advantages if you have access to their articles: they are one of the few
publishers to provide machine readable XML (many publishers do have XML versions of articles,
but do not provide it, as mentioned in the Introduction); they are one of the few (two)
publishers that take part in Crossref's text and data mining program. The packages
[fulltext][] and [crminer][] can be used to access Elsevier articles through Crossref's
TDM program. There's an interface to Scopus article search within [fulltext][].

@@

arXiv and bioRxiv are preprint publishers, the former in existence for many years, and the
latter new on the scene. Preprints are scholarly articles that are generally not
peer-reviewed, but that for the most part will later be published in a different peer-review
publication. You can access articles from these publishers through [fulltext][].
arXiv does provide a web API that we hook into; bioRxiv does not, but we can get you
articles nonetheless.

@@

Fatcat is a project from Ben Newbold of the Internet Archive Labs. It is a
"versioned, publicly-editable catalog of research publications:  journal articles,
conference proceedings, preprints, blog posts". Fatcat is currently does not have an
R client, but is used inside of the [fulltext][] package.

@@

## Learn more

To learn how to use the above packages, follow the links to get to documentation,
and how to report issues. The rOpenSci forum (<https://discuss.ropensci.org/>) is
a good place to ask questions about these packages.

@@

[fulltext][] is a general purpose R package for the data part of text mining:
search for articles, get links to articles, get article abstracts, and fetch
full text of articles. The `fulltext` package is always adding additional
data sources as time allows (See Table 1). Starting from searching for
articles, the outputs of search can be fed into a function to get links
to those articles, or to get abstracts for those articles, or to fetch
their full text. The following is a breakdown of the major distinct
parts of `fulltext`.

@@

Since users can go through a lot of article requests, we cache successfully
downloaded articles, and keep that knowledge consistent across R sessions; all
subsequent requests for the same article just use the cached version. Additionally,
all errors in `ft_get()` are collected in a data.frame in the output of the
function to help the user quickly determine what went wrong.

# Text mining in R: Use Cases

## Use cases in the literature

At least three papers have used the fulltext package. @Bauer2016 explored
a way to think about the qualitative impact of citations rather than simple
counts of citations; they did not use fulltext, but pointed it out as a good
option for collecting papers. @Walsh2018 used fulltext and [roadoi][], an
rOpenSci R package, to "map the literature" on nutritional interventions
in cognitive health. @Piper2019 in a review of DNA metabarcoding for
high-throughput insect surveillance used fulltext, along with [rentrez][]
(an rOpenSci package), to collect articles for text mining.

## Three case studies

The following three case studies demonstrate in brief how one could use
fulltext and related packages to do a few different text mining tasks.

### Case study 1: Citation mining

@@

### Case study 2: Abstract mining

@@

### Case study 3: Full text mining

@@

Text mining will always be a complex task given all the layers involved:
often temporal time-span of research questions; varied permissions among
researchers and their articles they're trying to access; varied approaches
to getting full text (xml vs pdf vs plain text); and more.

Programmatic text mining is a first step towards making text mining easier.
The R ecosystem is an especially good place to do text mining because
there are many packages for text mining analysis, and endless packages for
any required statistical analyses. In addition, rOpenSci and others are
building up a set of packages in R for searching for and acquiring full
text programatically to help make the research workflow as reproducible
as possible.

@@

With respect to what publishers can do to make text mining easier, publishers
should:

@@

This manuscript was greatly improved by comments from Maëlle Salmon.

@@

All scripts and data used in this paper can be found in the permanent
data archive Zenodo under the digital object identifier (DOI). This DOI
corresponds to a snapshot of the GitHub repository at
<https://github.com/ropensci/textmine>. Software can be found at
<https://github.com/ropensci>, all under MIT licenses.

@@

[rcrossref]: https://github.com/ropensci/rcrossref
[rorcid]: https://github.com/ropensci/rorcid
[fulltext]: https://github.com/ropensci/fulltext
[microdemic]: https://github.com/ropensci/microdemic
[arXiv]: https://github.com/ropensci/arXiv
[rdatacite]: https://github.com/ropensci/rdatacite
[rbhl]: https://github.com/ropensci/rbhl
[rentrez]: https://github.com/ropensci/rentrez
[rplos]: https://github.com/ropensci/rplos
[crminer]: https://github.com/ropensci/crminer
[europepmc]: https://github.com/ropensci/europepmc
[jaod]: https://github.com/ropensci/jaod
[jstor]: https://github.com/ropensci/jstor
[rcitoid]: https://github.com/ropenscilabs/rcitoid
[citecorp]: https://github.com/ropenscilabs/citecorp
[serrano]: https://github.com/sckott/serrano
[habanero]: https://github.com/sckott/habanero
[quanteda]: https://quanteda.io/
[pubchunks]: https://github.com/ropensci/pubchunks
[pdftools]: https://github.com/ropensci/pdftools
[libpoppler]: https://poppler.freedesktop.org/
[tesseract]: https://github.com/ropensci/tesseract
[rcoreoa]: https://github.com/ropensci/rcoreoa
[roadoi]: https://github.com/ropensci/roadoi
